Anonymous provision of services via blockchain

### 2022-03-03 access.tex
szymanski fixes and my patches

\title{Anonymous provision of services via blockchain}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski}\authorrefmark{1}}

\address[1]{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 Gdansk Poland (e-mail: stanislaw.baranski@pg.edu.pl}

\tfootnote{This paragraph of the first footnote will contain support 
information, including sponsor and financial support acknowledgement. For 
example, ``This work was supported in part by the U.S. Department of 
Commerce under Grant BS123456.''}

\markboth{Bara{\'n}ski : 
Anonymous provision of local services via blockchain}
{Bara{\'n}ski : 
Anonymous provision of local services via blockchain}

@@

We propose a framework for coordinating local anonymous service
provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.

A local service provider can employ our framework to provide
services without collecting any personal information. Possible
applications for this framework include anonymous clinical drug testing,
steroid testing, parenting testing, anonymous legal advice, or
anonymous financial trustworthiness evaluation.

In case of dispute, either due to exceeding deadlines or providing
incorrect results, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehaviour of the service
provider.

We analyse the protocol in the context of fairness and discuss further
extensions to an anonymous delivery system, payment with cash, and
decentralised conflict resolution system.

Our framework can enable various services currently based on unacceptable trust assumptions to the SP.
\end{abstract}

@@

Such user information can be used deliberately or unintentionally
(e.g., by theft) for insider disclosure, unauthorised access, or
commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.

@@

The guarantee of the privacy of the data is often based merely on a trust assumptions and security of IT system. However, most of the SP do not need the personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.

@@

Example services that would benefit from anonymous services are:
\begin{itemize}
    \item Patients willing to take a steroid test, drug tests, venereal diseases test, paternity test — have strong incentive to keep the whole procedure private. Merely the fact that they took the test — without exposing the results — is suggestive enough to act as a premise in case of a conflict.

Especially celebrities, politicians and public figures are prone to this kind of problem as such precedent can negatively influence their future career.

Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorised actor (both curious employee, and malicious attacker).

Our protocol allows taking such tests anonymously and therefore getting
rid of the strong trust assumption put on the laboratories and their IT
systems.
\item People willing to take business action that may be risky or not yet fully legislated, may be willing to receive the risk estimation and prediction of possible repercussions of such action.

@@

Our protocol would allow taking such advices anonymously, and therefore
getting rid of the strong trust assumption put on the lawyers and their IT systems.
\end{itemize}

We propose a framework for anonymously provisioning services that require delivery of physical materials. A service provider employing our framework can provide services without collecting any personal information from customers.

In case of dispute, either due to exceeding deadlines or providing
incorrect results, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehaviour of the service
provider.

To achieve these objectives we use:
\begin{itemize}
    \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
    \item Message board blockchain, to achieve fairness, i.e., as a mean for proving that certain actions took place at a certain moment of time without the trusted third party.
    \item Content-addressable peer-to-peer storage network, to provide results to the customer. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption: to encrypt and decrypt results published on public networks.
        \item Digital signatures: To achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

In our case the customer is exchanging with the SP cryptocurrency and materials for the results.

\paragraph{Contributions}
We contribute to the field of fair-exchanges by proposing a simple,
practical, and anonymous framework that does not rely on centralised trusted-third party, but on decentralised blockchain and
distributed content-addressable storage network.

@@

Our framework simultaneously provides five main properties:

\begin{itemize}
\item Anonimity:
throughout the whole transaction the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivised to act accordingly to the protocol; otherwise the misbehaving party ends up in worst position.
\item Dispute resolution: at each step of the protocol the customer can open a dispute win the case iff the SP misbehaved.
\item TTP-less: 
our protocol does not rely on trusted-third party to conduct transactions in fairly manner. Only in case of dispute the centralised justice is invlolved (the justice decentralisation is discussed in section ~\ref{sec:future-work}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge we
are the first to propose a system that satisfy all five properties
stated above. Especially anonimity and physical materials delivery, are
properties that were rarely addressed together, and if so, the protocol
based on TTP, and strong and impractial assumptions on banking system~\cite{birjoveanu2015anonymity}, or didn't address the of conflict
between parties~\cite{altawy2017lelantos}.

Our framework can potentially enable variety of services that for many
customers base on unacceptable trust assumptions to the SP.

\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we briefly review related works. 
Section~\ref{sec:background} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
Section~\ref{sec:protocol} describes how the protocol works in details.
Section~\ref{sec:fairness-analysis} provides an fairness analysis of the proposed protocol.
Section~\ref{sec:future-work} discuss possible improvements. 
Finally, section~\ref{sec:conclusion} concludes the paper.

@@

\paragraph{Anonymity and Fair-Exchange in e-Commerce Protocol for Physical Products Delivery} \label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

Authors of~\cite{birjoveanu2015anonymity} proposed a
fair-exchange of physical product and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by
introducing online trusted third party that validate coins and provide
fair exchange guarantees.

The anonymity is ensured by assuming the existence of source cabinet
(SC) and delivery cabinet (DC), and a trusted delivery agent who take
product from a source cabinet and provide it to a destination cabinet.
Both cabinets provides access to the product by passwords to conceal
identity of the customer and the merchant. To avoid identity disclosure
of customer and merchant, the access to the product is provided by
passwords.

@@

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The customer buys a digital coin from his bank and validates it with the TTP.
    \item The customer sends to the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
    \item The merchant post the product to the source cabinet.
    \item Delivery agent collect the product from source cabinet and post it to delivery cabinet.
    \item Customer collects the product from delivery cabinet using password.
    \item The customer checks if the product is actually the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the customer sends the acknowledge to delivery cabinet and decryption key to the merchant.
        \item The merchant redeem the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the delivery cabinet is equipment with video camera that records the moment when the customer open the package and let the customer to signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item the dispute is settled via TTP, optionally letting each party to reveal it's identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

@@

\begin{itemize}
    \item the TTP does not misbehave or collude with any party. 
    \item The customer's and merchant's banks enable confidental transactions and both share commit-buffer where the value is locked until the transaction is finished.   
    \item All banks mantain a global list of coin's serial numbers to prevent double-spending problem. 
    \item The source cabinet and delivery cabinet exists, and in both the product access is protected by password.
    \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package, and provide a way to submit the video to TTP in case of a dispute. 
    \item There exists a trusted delivery agent.
    \item Communication channels between parties provides anonymity.
\end{itemize}

\paragraph{Themis: Towards decentralized escrow of cryptocurrencies without trusted third parties}\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}

Themis~\cite{meng2019themis} is a fair-exchange
protocol, which uses blockchain instead of TTP. It provide escrow
services for secure exchanging between cryptocurrencies and digital goods, and decentralised dispute resolution system for resolving conflicts.

Two parties, say Alice and Bob, can create an escrow by generating
2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account
using Thresh-Key-Gen protocol. Alice and Bob generate secret keys
\(x_A\) and \(x_B\) accordingly, the shared account public key becomes
\(y = g^{x_A+x_B}\); only the access to both Alice's and Bob's secrets
grants access to the shared account.

Then, both Alice and Bob, takes their keys, and split them into
\(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
\(n\) is the number of mediators that participate in the decentralised
network, and \(t+1\) becomes the threshold of sufficient number of
mediators that can reconstruct the secret key.

@@

In case of dispute, the decentralised network of mediators settle the
conflict and grand one winning party, the other party secret key,
letting him to withdraw the funds.

The honesty of mediators is achieved by the monetary incentivisation and
reputation system.

\paragraph{Lelantos: A blockchain-based anonymous physical delivery system}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}

Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous
physical delivery system. The anonymity is achieved by employing ToR's
onion routing to connect physical delivery providers. The whole route
from merchant to customer is split into multiple steps, and each step is
undertaken by different randomly selected delivery provider. As long as
the develiery providers does no collude, mechant can not learn both
identity and destination address of the customer.

Onchain smart-contract is used to coordinate the whole process and
mediate communication between customer and delivery providers.

@@

\section{Background}\label{sec:background}
\subsection{Dispute resolution system}

Disputes are inevitable part of all human transactions. Whether intentional or accidental, the system should prevent any behaviour volatiling rules of agreed contract or local jurisdiction. The rules are specified by law, and implemented by police.

The vision of smart contract was to replace legal contract with
programmable and autonomous contracts. The specifications of contract
was encompasses in the code, hence the slogan ``code as a law''. Yet,
the blockchain paradigm has its limitations. It can assure the
correctness of data existing on the blockchain. The problem arises on
the contact between blockchain and real world. When we want the smart
contract to make a decision based on some input from outside the
blockchain. We move a lot of trust assumptions on the data providers.
The technique of providing real world data to the blockchain is called
oracle. Oracle provide data based on decentralised network of mediators,
therefore the trust is also decentralised.

Some oracles provide the data like weather, soccer match result, stock
price, train delay, election results, others---and they are the ones we
are interested in---provide the settlement of a submited dispute.

Themis~\cite{meng2019themis} besides providing fair-exchange protocol,
also offers a semi-autonomous decentralised dispute resolution system,
which comply with the web3 postulates of decentralised web. Themis
resolve disputes by set of voluntary anonymous mediators participating
in a voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivisation and reputation
system.

Kleros~\cite{lesaege2018kleros} is a smart contract deployed on
Ethereum platform that mimics in decentralised and autonomous way how
court works in real life. In Kleros, every process of a dispute like
gathering evidences, selecting jurors, rewarding the winning party is if
automated by a set of smart contracts. Simillar to Themis, the honesty
of the agents voting in a case is achieved by game-theoretical economic
incentives.

@@

In case of dispute the customer can proof to justice (police, court, etc.) convincing evidences for the honesty of the customer and misbehaviour of the SP. 
Because the customer is anonymous the SP can not start a dispute---there is no mean to identify the customer.

To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in advantage position, therefore he has no reason to start a dispute. The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

Abstracting from the services the SP is providing, in case of dispute each party should be able to prove its honest behaviour. We introduce three proofs that should be disclosed to justice in case of a dispute:

\begin{enumerate}
    \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it. It consists of: current time; deadline to pay for the transaction; and deadline to provide the service; deadline to provide the service results; randomly generated number uniquely identifying the transaction; and the SP's signature guaranteeing non-repudiation. The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.

@@

    \item Proof-of-provision ($\mathrm{PoP}$) is an proof that the SP published the results at a certain time. It defend the SP in case the customer unjustly start a dispute after the results has been published. It consist of: content identifier as specified in section ~\ref{storage-network}; the value uniquely identifying the transaction previosuly generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication. The connection between $\mathrm{PoP}$ and the results is made by the content identifier which uniquely points to the results such that the $\mathrm{PoP}$ can not forge results after the publication.
\end{enumerate}

@@

The idea behind proof-of-existence is to certify that some information
has existed at a certain moment of time, in such a way that nobody can
undermine its existence, integrity, and ownership (also called the
non-repudiation requirement).

@@

We let keep the protocol general enough to let the implementer use any
existing technology to provide message board service, with the
assumption that it's decentralised and supports subscribing for the
upcoming proofs from particular address.

@@

Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambigous definitions~\cite{smith2011information}. For the purpose of our work we rely on more concrete definitions, i.e.~confidentality and anonymity.

Confidentality is the ability to hide the details of an action from others. Or we can say, that the system guarantee confidentality if for all observers everything they can say about the action is the fact that it happened and nothing more.

Anonymity is a the ability to hide one identity from others. More precisely, the unability to correlate actions performed within the system with the identity of the user. Or we can say, that the system guarantee anonymity if for all observers the actions are equally likely to be associated with any user of the system. However, anonymity is a spectrum rather than dichotomous classification. One method of quantifying level of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}. It measure the user's anonymity by the number of other users from whom the user can not be distinguished. Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users. The larger \textit{k}, the higher anonymity.

There are also techniques that can be deployed on non-anonymous blockchains, the so called mixers that literally gather together users into an \textit{anonymity set}, which then collude together in order to launder the transactions, in such a way that to a observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.

Some systems guarantee pseudonomity rather than anonymity. Pseudonomity, allows uses to hide their real identity behind the pseudonym. Despite the whole system is transparent and allows linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret. This assumption is hard to satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges. This makes the anonymity of the user dependent on the security of the IT system. Moreover, some correlations can be infered merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.

The relations between these terms are ilustrated in the figure~\ref{fig:anonymity-diagram}.

\begin{figure}[h!]
\caption{Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP. Alice controls two addresses 1 and 2, the connection between her real identity and the first address was compromised, and therefore the identification is possible, the connection between the second pseudonym is still unknown therefore anonymous. Alice takes two actions; the first one from the compromised address and the second one from anonymous one. The first action is confidential; therefore even though the psudonym has been compromised the action can not be associated with the Alice. The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.}
\centering
\includegraphics[width=9cm]{anonymity-diagram.png}
\label{fig:anonymity-diagram}
\end{figure}

@@

\subsection{Payment for services}\label{payment-for-services}
Transactions between customers and SP have to be somehow pegged in order
to prevent proving one payment for multiple transactions. In other
words, we need some way to uniquely link particular payment with the
transaction it pays for.

Depending for the cryptocurrency the link can be created in different
ways:

@@

\section{The Protocol}\label{sec:protocol}

>>>>

\title{Anonymous provision of services via blockchain}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski}\authorrefmark{1},
\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
 }

\address[1]{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 Gdansk Poland (e-mail: stanislaw.baranski@pg.edu.pl, julian.szymanski@eti.pg.edu.pl}

\tfootnote{The work has been supported partially by the founds of Department of Computer Architecture Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.}

\markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Anonymous provision of local services via blockchain}
{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Anonymous provision of local services via blockchain}

@@

We propose a protocol for coordinating local anonymous service
provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.

A local service provider can employ our protocol to provide
services without collecting any personal information. Possible
applications for this protocol include anonymous clinical drug testing,
steroid testing, parenting testing, anonymous legal advice, or
anonymous financial trustworthiness evaluation.

In case of dispute, either due to exceeding deadlines or providing
incorrect results, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehavior of the service
provider.

We analyze the protocol in the context of fairness and discuss further
extensions to an anonymous delivery system, payment with cash, and
decentralized conflict resolution system.

Our protocol can enable various services currently based on unacceptable trust assumptions to the SP.
%JS to framework czy protocol?
%SB zmieniłem na protocol, framework jest zbyt abstrakcyjne
\end{abstract}

@@

Such user information can be used deliberately or unintentionally
(e.g., by theft) for insider disclosure, unauthorized access, or
commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.

@@

The guarantee of the privacy of the data is often based merely on trust assumptions and the security of IT system. However, most of the SP does not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.

@@

There is some services that would benefit from anonymous services, some examples are:
\begin{itemize}
    \item Patients willing to take a 
    test for drug, venereal diseases, paternity etc. have a strong incentive to keep the whole procedure private. Merely the fact that they took the test — without exposing the results — is suggestive enough to act as a premise in case of a conflict.

Especially celebrities, politicians, and public figures are prone to this kind of problem as such precedent can negatively influence their future career.

Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorized actor (both curious employee, and malicious attacker).

Our protocol allows taking such tests anonymously and therefore getting
rid of the strong trust assumption put on the laboratories and their IT
systems.
\item People willing to take business activities that may be risky % or not yet fully legislated, 
may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.

@@

Our protocol would allow taking such advice anonymously, and therefore
getting rid of the strong trust assumption put on the lawyers and their IT systems.
\end{itemize}

We propose a protocol for anonymously provisioning services that require the delivery of physical materials. A service provider employing our protocol can provide services without collecting any personal information from customers.

In case of dispute, either due to exceeding deadlines or providing
incorrect results, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehavior of the service 
provider.
%JS a np automatyczny zwrot środków?
%SP to wymagałoby wprowadzenie depozytu co bardzo komplikuje cały system. Co więcej miałoby to sens tylko wtedy gdyby użyć "zdecentralizowanych sądów" (Future Work/Justice).

To achieve these objectives we use:
\begin{itemize}
    \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party.
    \item Content-addressable peer-to-peer storage network, to provide results to the customer. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption: to encrypt and decrypt results published on public networks.
        \item Digital signatures: To achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

In our case, the customer is exchanging with the SP cryptocurrency and materials for the results.

%\paragraph{Contributions}
We contribute to the field of fair-exchanges by proposing a simple,
 practical, and anonymous protocol that does not rely on centralized trusted-third party, but on decentralized blockchain and
distributed content-addressable storage network.

@@

Our protocol simultaneously provides five main properties:

\begin{itemize}
\item Anonymity:
throughout the whole transaction, the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in the worst position.
\item Dispute resolution: at each step of the protocol the customer can start a dispute and win the case if and only if the SP misbehaved.

\item TTP-less: 
our protocol does not rely on a trusted-third party to conduct transactions in fairly manner. Only in case of dispute   the centralized justice is involved (the justice decentralization is discussed in section ~\ref{sec:future-work}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge we
are the first to propose a system that satisfies all five properties
stated above using blockchain technology. Especially anonymity and physical materials delivery, are
properties that were rarely addressed together, and if so, the protocol
based on TTP, and strong and impractical assumptions on banking system~\cite{birjoveanu2015anonymity}, or didn't address the conflict
between parties~\cite{altawy2017lelantos}.

Our protocol can potentially enable a variety of services that for many
customers based on unacceptable trust assumptions to the SP.

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we briefly review related works. 
Section~\ref{sec:building-blocks} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:future-work} discuss possible improvements. 
Finally, section~\ref{sec:conclusion} concludes the paper.

@@

\subsection{Fair-exchange and blockchain}
The idea of certified mail is simple, neither the sender can deny sending the mail, nor the receiver can deny receiving it. As the service is widely used in paper world, achieving it for e-mails haven't meet the agreement across scientific community for over 40 years. The main reason was the dependency of TTP, which significantly reduce the performance, security, and robustness of such protocols. The protocols that do not use TTP struggle with high computation and communication overhead.

Authors of ~\cite{hinarejos2019solution} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation), which acts as a secure, verifiable, and decentralized TTP.

The idea behind certified e-mails—and any other fair-exchange protocol—is following:
\begin{enumerate}
    \item The sender sends encrypted and signed message to the receiver.
    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publish on blockchain (or TTP in general) a proof of delivery and the decryption key.
    \item The receiver decrypts the encrypted message using the published decryption key.
\end{enumerate}

The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior having access to the decrypted message. And the sender publishing the decription key together with the proof of delivery on blockchain (or TTP) so that the receiver can not deny both receiving the message and having access to decryption key, because it is publicly available.

The protocol also handles confidentiality — the encryption key used to encrypt and then decrypt the message is encrypted using the receiver's public key, so the key is never published in raw form.
Also, the protocol supports timeliness, meaning that the transaction is always finalized in a finite time.

In this case, the role of Blockchain is to attest the public existence of decryption key at a particular point of time.

\subsection{Fair-exchange, anonymity, and physical products delivery} 
\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

Authors of~\cite{birjoveanu2015anonymity} proposed a
fair-exchange of physical products and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by
introducing online trusted third parties that validate coins and provide
fair exchange guarantees.

The anonymity is ensured by assuming the existence of a source cabinet
(SC) and delivery cabinet (DC), and a trusted delivery agent who take
a product from a source cabinet and provide it to a destination cabinet.
Both cabinets provide access to the product by passwords to conceal
the identity of the customer and the merchant. To avoid identity disclosure
of customers and merchants, the access to the product is provided by
passwords.

@@

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The customer buys a digital coin from his bank and validates it with the TTP.
    \item The customer sends to the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
    \item The merchant post the product to the source cabinet.
    \item Delivery agent collects the product from the source cabinet and posts it to the delivery cabinet.
    \item Customer collects the product from the delivery cabinet using a password.
    \item The customer checks if the product is the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the customer sends the acknowledge to the delivery cabinet and decryption key to the merchant.
        \item The merchant redeem the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

@@

\begin{itemize}
    \item the TTP does not misbehave or collude with any party. 
    \item The customer's and merchant's banks enable confidential transactions and both share commit-buffer where the value is locked until the transaction is finished.   
    \item All banks maintain a global list of coin's serial numbers to prevent double-spending problems. 
    \item The source cabinet and delivery cabinet exist, and in both the product access is protected by a password.
    \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute. 
    \item There exists a trusted delivery agent.
    \item Communication channels between parties provide anonymity.
\end{itemize}

\subsection{Fair-exchange, blockchain, and decentralized dispute resolution}
\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}

Themis~\cite{meng2019themis} is a fair-exchange
protocol, which uses blockchain instead of TTP. It provides escrow
services for secure exchanging between cryptocurrencies and digital goods, and a decentralized dispute resolution system for resolving conflicts.

Two parties say Alice and Bob, can create an escrow by generating
2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account
using Thresh-Key-Gen protocol. Alice and Bob generate secret keys
\(x_A\) and \(x_B\) accordingly, the shared account public key becomes
\(y = g^{x_A+x_B}\); only the access to both Alice's and Bob's secrets
grants access to the shared account.

Then, both Alice and Bob, take their keys, and split them into
\(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
\(n\) is the number of mediators that participate in the decentralized
network and \(t+1\) becomes the threshold of a sufficient number of
mediators that can reconstruct the secret key.

@@

In case of dispute, the decentralized network of mediators settle the
conflict and grand one winning party, the other party secret key,
letting him withdraw the funds.

The honesty of mediators is achieved by the monetary incentivization and
reputation system.

\subsection{Blockchain, anonymity, and physical delivery}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}

Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous
physical delivery system. The anonymity is achieved by employing ToR's
onion routing to connect physical delivery providers. The whole route
from merchant to a customer is split into multiple steps, and each step is
undertaken by the different randomly selected delivery providers. As long as
the delivery providers do not collude, a merchant can not learn both
the identity and destination address of the customer.

Onchain smart-contract is used to coordinate the whole process and
mediate communication between customers and delivery providers.

@@

%JS moze\section{Building Blocks}
%SB Dla mnie idealnie.
\section{Building Blocks}\label{sec:building-blocks}
%JS bacground czego?  
%SB To jest takie wprowadzenie i opisanie wszystkich elementów które będą potrzebne do stowrzenia protokołu. Czy Preliminaries będzie ok?
\subsection{Dispute resolution system}

Disputes are an inevitable part of all human transactions. Whether intentional or accidental, the system should prevent 
violation of  
agreed contract rules  or local jurisdiction. The rules are specified by law and implemented by the police.

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The specifications of the contract
were encompassed in the code, hence the slogan ``code as a law''. Yet,
the blockchain paradigm has its limitations. It can assure the
correctness of data existing on the blockchain. The problem arises in
the contact between blockchain and the real world. When we want the smart
contract to make a decision based on some input from outside the
blockchain. We move a lot of trust assumptions on the data providers.
The technique of providing real-world data to the blockchain is called
oracle. Oracle provides data based on a decentralized network of mediators,
therefore the trust is also decentralized.

Some oracles provide the data like weather, soccer match result, stock
price, train delay, election results, others---and they are the ones we
are interested in---provide the settlement of a submitted dispute.

Themis~\cite{meng2019themis} besides providing fair-exchange protocol,
also offers a semi-autonomous decentralized dispute resolution system,
which complies with the web3 postulates of a decentralized web. Themis
resolve disputes by a set of voluntary anonymous mediators participating
in voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

Kleros~\cite{lesaege2018kleros} is a smart contract deployed on
Ethereum platform mimics in a decentralized and autonomous way how
the court works in real life. In Kleros, every process of a dispute like
gathering evidence, selecting jurors, rewarding the winning party is 
automated by a set of smart contracts. Similar to Themis, the honesty
of the agents voting in a case is achieved by game-theoretical economic
incentives.

@@

In case of dispute, the customer can prove to justice (police, court, etc.) convincing evidence for the honesty of the customer and misbehavior of the SP. 
Because the customer is anonymous the SP can not start a dispute---there is no means to identify the customer.

To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position, therefore he has no reason to start a dispute. The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.

Abstracting from the services the SP is providing, in case of a dispute each party should be able to prove its honest behavior. We introduce three proofs that should be disclosed to justice in case of a dispute:

\begin{enumerate}
    \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it. It consists of the current time; deadline to pay for the transaction, and the deadline to provide the service; deadline to provide the service results; randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation. The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.

@@

    \item Proof-of-provision ($\mathrm{PoP}$) is proof that the SP published the results at a certain time. It defends the SP in case the customer unjustly starts a dispute after the results have been published. It consists of a content identifier as specified in section ~\ref{storage-network}; the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication. The connection between $\mathrm{PoP}$ and the results is made by the content identifier which uniquely points to the results such that the $\mathrm{PoP}$ can not forge results after the publication.
\end{enumerate}

@@

The idea behind proof-of-existence is to certify that some information
has existed at a certain moment, in such a way that nobody can
undermine its existence, integrity, and ownership (also called the
non-repudiation requirement).

@@

We let keep the protocol general enough to 
be implemented using any of  
existing technology to provide message board service, with the
the assumption that it's decentralized and supports subscribing for the
upcoming proofs from a particular address.

@@

Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambiguous definitions~\cite{smith2011information}. For our work we rely on more concrete definitions, i.e.~confidentality, and anonymity.

Confidentiality is the ability to hide the details of action from others. Or we can say, that the system guarantees confidentiality if for all observers everything they can say about the action is the fact that it happened and nothing more.

Anonymity is the ability to hide one identity from others. More precisely, the inability to correlate actions performed within the system with the identity of the user. Or we can say, that the system guarantees anonymity if for all observers the actions are equally likely to be associated with any user of the system. However, anonymity is a spectrum rather than a dichotomous classification. One method of quantifying the level of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}. It measures the user's anonymity by the number of other users from whom the user can not be distinguished. Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users. The larger \textit{k}, the higher anonymity.

Some techniques can be deployed on non-anonymous blockchains, the so-called mixers that gather together users into an \textit{anonymity set}, which then collude together to launder the transactions, in such a way that to an observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.

Some systems guarantee pseudonomity rather than anonymity. Pseudonomity allows users to hide their real identity behind the pseudonym. Despite the whole system being transparent and allowing linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret. This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges. This makes the anonymity of the user dependent on the security of the IT system. Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.

The relations between these terms are illustrated in the figure~\ref{fig:anonymity-diagram1}.

\begin{figure}[h!]
\includegraphics[width=9cm]{anonymity-diagram.png}
\centering
\caption{Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP. Alice controls two addresses 1 and 2, the connection between her real identity and the first address was compromised, and therefore the identification is possible, the connection between the second pseudonym is still unknown therefore anonymous. Alice takes two actions; the first one from the compromised address and the second one from anonymous one. The first action is confidential; therefore even though the psudonym has been compromised the action can not be associated with the Alice. The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.}

\label{fig:anonymity-diagram1}
\end{figure}

@@

\subsection{Payment for services}\label{payment-for-services}
Transactions between customers and SP have to be somehow pegged to prevent proving one payment for multiple transactions. In other
words, we need some way to uniquely link particular payment with the
the transaction paid for.

Depending on the cryptocurrency the link can be created in different
ways:

@@

%%%%%%%%%%% dotad sprawdzone
\section{The Protocol}\label{sec:protocol}
